---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->
[![R build status](https://github.com/jayrobwilliams/RWmisc/workflows/R-CMD-check/badge.svg)](https://github.com/jayrobwilliams/RWmisc/actions)
[![codecov](https://codecov.io/gh/jayrobwilliams/RWmisc/branch/master/graph/badge.svg)](https://codecov.io/gh/jayrobwilliams/RWmisc)
[![License](http://img.shields.io/badge/license-GPL%20%28%3E=%203%29-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-3.0.html)
<!-- badges: end -->

# RWmisc

This package contains convenience functions I have written to help deal with
spatial data spread across multiple UTM zones and aggregating raster data to
overlapping polygons.

# Installation

You can install the latest development version from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("jayrobwilliams/RWmisc")
```

# Examples

The functions contained in this package serve to make working with spatial data
on large scale easy, as when carrying out cross-national analyses with spatial
data. The function `projectUTM` can project `sf` and `sp` objects in latitude,
longitude coordinate reference systems, and can even re-project
already-projected objects in other projected coordinate reference systems.

```{r projectUTM}
library(sf)

library(RWmisc)

nc <- st_read(system.file("shape/nc.shp", package="sf"))

projectUTM(nc)
```

The `theme_rw` function is the minimalist theme I often use for figure in my
work. While it is useful for standard plots, it is an especially large
improvement over the `ggplot2` defaults for maps.

```{r theme_rw, fig.show = 'hold'}
library(ggplot2)

ggplot(aes(fill = BIR74), data = nc) +
  geom_sf()

ggplot(aes(fill = BIR74), data = nc) +
  geom_sf() +
  theme_rw()
```

